\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{tgpagella}
\usepackage{mathtools}
\usepackage{geometry}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{float}
\usepackage{apptools}
%\usepackage{units}
\usepackage{tocloft}
\usepackage{physics}
\usepackage[labelfont=bf]{caption}
\usepackage[noabbrev,capitalize]{cleveref}

\usepackage[acronym,toc]{glossaries}
\loadglsentries{acros}


\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=magenta,
    urlcolor=blue,
    citecolor=black
}

\usepackage[backend=biber,style=numeric,sorting=nyt,
	natbib=true,firstinits=true,uniquename=false,defernumbers=true]{biblatex}

\addbibresource{../spectral-elements.bib}

% --------------------------------------------------------------------
% Convenience commands
% --------------------------------------------------------------------
\newcommand{\ohat}{\hat{\Omega}}
\newcommand{\rvec}{\mathbf{r}}
\newcommand{\psifullprime}{\psi\left(\mathbf{r},\hat{\Omega}',E',t\right)}
\newcommand{\psifull}{\psi\left(\mathbf{r},\hat{\Omega},E,t\right)}
\newcommand{\psisimple}{\psi\left(\mathbf{r},\hat{\Omega}\right)} % "psi simple"
\newcommand{\psiplus}{\psi^+}
\newcommand{\intelems}{\int_{\mathcal{A}}\int_{\tau}}
\newcommand{\elemdifs}{\dd \tau \dd \ohat}
\newcommand{\sigt}{\Sigma_t}
% --------------------------------------------------------------------


\newcommand{\Sn}{$S_N$}
\newcommand{\Pn}{$P_N$}

\title{\textbf{Spectral Elements in Neutron Transport\\Literature Notes}}
\author{L. Pohlmann}
\date{Last Modified: \today}

\begin{document}
\maketitle
\tableofcontents
\printglossary[type=\acronymtype]

\section{A Self-Adjoint Angular Flux Equation~\cite{morelSelfAdjointAngularFlux1999}}
\begin{itemize}
    \item ``The traditional self-adjoint forms of the transport equation are the even- and odd-parity equations.''
    \item Advantages of even- and odd-parity equations:
          \begin{itemize}
              \item Can be solved on multidimensional finite element spatial meshes using standard techniques.
              \item Implementation of continuous finite element spatial discretizations results in matrices that are \gls{spd}.
              \item \Pn equations are more easily solved in the second-order self-adjoint form than the first-order form because the flux moments are strongly coupled via the streaming operator ($\ohat\cdot\grad$)
          \end{itemize}
    \item Disadvantages of even- and odd-parity equations:
          \begin{itemize}
              \item The source iteration equations in \Sn create a \textit{general} sparse matrix rather than a block lower-triangular matrix, so sweeping cannot be implemented. As noted, this is not necessarily a drawback, as whether or not sweeping is more efficient depends on the mesh (an orthogonal mesh will see significant improvements using sweeping).
              \item ``In multidimensions, reflective and reflective-like boundary conditions result in fully implicit coupling between incoming and outgoing directions. In contrast, only on-way coupling occurs between ... directions with the standard first-order form of the transport equation.'' This causes \gls{dsa} techniques to lose efficacy in \Sn. \Pn, however, sees no losses because angular moments are always coupled at the boundaries.
              \item ``The full angular flux is difficult to numerically calculate because the even- and odd-parity flux components can be obtained with different orders of accuracy and are no spatially co-located. This arises because one component is always proportional to the gradient of the other.''
              \item The streaming term contains the inverse of the total cross section, which produces a singularity for streaming in a void. As noted, it is possible to derive even- and odd-parity equations specifically for streaming in a vacuum, but they come without coupling to each other. This means that to truly avoid the singularity, one would need to solve \textit{both} equations to get the angular in a vacuum.
              \item The matrix produced in a region that is purely scattering is singular.
          \end{itemize}
          Advantages of the \gls{saaf} equation \textit{in addition to those listed above for the even- and odd-parity equations}:
          \begin{itemize}
              \item Angular flux is directly solved for (rather than needing to reconstruct from the parity solutions).
              \item Reflective and reflective-like boundary conditions are coupled the same way as they are in the standard first-order transport equation, and thus are much simpler to implement with \Sn.
              \item Can be solved in a void.
          \end{itemize}
          Disadvantages of the \gls{saaf} equation (independent of the above):
          \begin{itemize}
              \item Cannot be swept for source iterations (for the same reason as above).
              \item Cannot be solved in a purely-scattering region (for the same reason as above).
              \item Angular domain is the full unit sphere (as opposed to only a half of the unit sphere in the even- and odd-parity equations).
          \end{itemize}
    \item \Gls{saaf} equation is:
          \begin{equation}\label{eq:saaf-equation}
              -\ohat\cdot \grad \left(\frac{1}{\Sigma_t-S}\right)\ohat\cdot \grad \psi+\left(\Sigma_t-S\right)\psi = q-\ohat\cdot \grad \left(\frac{1}{\Sigma_t-S}\right)q
          \end{equation}
          where $q$ is an inhomogenous volumetric source, $S$ is the inscatter operator \begin{equation} \label{eq:scatter-operator}
              S\psi=\int_{4\pi}\Sigma_s \left(\ohat\cdot\ohat '\right)\psi\left(\ohat '\right)\dd \ohat '
          \end{equation}.
    \item Because \cref{eq:saaf-equation} is second-order in space, we now require an additional boundary condition. The natural incoming flux boundary condition is:
          \begin{equation*}
              \psi\left(\rvec_b,\ohat \right) = f(\ohat),\quad \ohat\cdot \hat{n}<0
          \end{equation*}
          (note that $f\left(\ohat\right)=0$ for vacuum BC). In addition, we require \cref{eq:saaf-equation} to satisfy the first-order transport equation on the boundary for outgoing fluxes:
          \begin{equation*}
              \ohat\cdot\grad\psi\left(\rvec_b,\ohat\right)+\Sigma_t\psi\left(\rvec_b,\ohat\right)=S\psi\left(\rvec_b,\ohat\right)+q\left(\rvec_b,\ohat\right),\quad \ohat\cdot\hat{n}>0.
          \end{equation*}
    \item Energy-dependent versions of the operator $\frac{1}{\Sigma_t-S}$ are usually not self-adjoint, meaning the discretized \gls{saaf} equations are no longer \gls{spd}. To keep this property, the multigroup approximation is made.
    \item Handling of void regions in the \gls{saaf} equation is still problematic. This paper suggests additional research should be done for this\ldots
    \item Spherical harmonics functions are eigenfunctions of the monoenergetic scattering operator, \cref{eq:scatter-operator}. (Derivation included in paper.)
\end{itemize}


\clearpage
\printbibliography

\end{document}
